LAGOS lake depth

### 2020-02-20 README.Rmd
formatting
rm a lot of the non bathy files and info

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

## LAGOS-US-Depth: Lake depth at continental scales

### Data (see [data/lagosus_depth.csv](data/lagosus_depth.csv))

```{r echo=FALSE}
# see scripts/99_make_taxonomy.R

dt <- read.csv("data/lagosus_depth_taxonomy.csv", stringsAsFactors = FALSE)

knitr::kable(setNames(dt, c("Variable name", "Description")))
```

@@

>>>>

```{r, echo = FALSE}
library(details)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

## Bathymetry manuscript

@@

Data: [bathymetry derived lake depth](data/00_bathy_depth/00_bathy_depth.csv)

```{details, echo=FALSE, details.summary = "Data dictionary"}
# see scripts/99_make_taxonomy.R

dt <- read.csv("data/00_bathy_depth/00_bathy_depth.csv", stringsAsFactors = FALSE)
knitr::kable(setNames(data.frame(names(dt)), "field"))
```

Data: [bathymetry derived lake geometry](data/00_bathy_depth/bathy_geometry.csv)

```{details, echo=FALSE, details.summary = "Data dictionary"}
# see scripts/99_make_taxonomy.R

dt <- read.csv("data/00_bathy_depth/bathy_geometry.csv", stringsAsFactors = FALSE)
knitr::kable(setNames(data.frame(names(dt)), "field"))
```
